---
title: "R Lab 3: Chi-square Goodness of Fit Test in R"
subtitle: "Is the census report accurate?"
author:
  - "Team Captain: NAME HERE"
  - "Facilitator: NAME HERE"
  - "Recorder: NAME HERE"
  - "Resource Manager: NAME HERE"
date: "DATE HERE"
format: pdf
editor: source
execute:
  echo: true
  error: true
  message: false
  warning: false
---

0.  **Load the `infer` package below `library(tidyverse)`**

```{r setup}
# Load in the packages necessary for our analysis: tidyverse, infer
library(tidyverse)
library(infer)
```

The accuracy of a census report for a city in southern California was questioned by some government officials. A random sample of 1,215 people living in the city was used to check the census report. The census results (expected probabilities) are given below:

**Census Results**

+ Black: 10%
+ Asian: 3%
+ Anglo: 38%
+ Latino/Latina: 41%
+ Indigenous: 6%
+ All others: 2%

**Research question:** Do the counts obtained via the random sample call into question the accuracy of the census report?

1.  **Read in the data and call it `ca_sample`. Additionally, print the top 6 rows to inspect your data.**

```{r read-data}
ca_sample <- read_csv("data/census_sample.csv")
```

2.  **What is the observational unit for this study?**

    A resident of the city.

3.  **Create a summary table of the number of individuals in the sample who self-identified with each ethnic `origin`.**

```{r summary-table}
ca_sample |> 
  count(origin)
```

4.  **Using the skills you learned class last week, create a bar plot of the observed *proportions* of individuals in our sample who self-identified with each ethnic `origin`.**

```{r bar-plot}
ggplot(data = ca_sample,
       mapping = aes(x = origin)
       ) +
  geom_bar(stat = "count",
           aes(y = ..prop.., group = 1)
           ) +
  labs(title = "Is the census report correct?",
       x = "Ethnic Origin",
       y = "Proportion of Residents"
       )
```

5.  **Notice the ordering of origin categories. Why do you think "All others" is first and "Latino/Latina" is last in our list?**

    Alphabetical order.

6.  **As a statistician, Lily questions the "All others" category. What might be some data and ethical concerns surrounding reporting and aggregating data in this way?**

    This could unintentionally marginalize certain groups by treating minority groups as "the same". We want to be cautious about the implications of our data.

7.  **Write the null and alternative hypotheses for investigating this research question.**

    Null: The distribution of ethnic origin for individuals in the city matches the distribution of ethnic origin reported by the census.

    Alternative: The distribution of ethnic origin for individuals in the city differs from the distribution of ethnic origin reported by the census.
    
    
or...

    Null: The proportions of ethnic origins for all city residents is equal to those reported by the census.

    Alternative: At least one of the proportions of ethnic origins for all city residents is different from that reported by the census.

or... could write out in symbols setting equal to the expected proportions.

8.  **How many of the 1,215 people do we expect to see of each ethnic origin if the results of the census are accurate?**

**Expected Counts**

+ Black: 121.5
+ Asian: 97.2
+ Anglo: 461.7
+ Latino/Latina: 498.15
+ Indigenous: 72.9
+ All others: 24.3

*Note: we use the expected counts to check our conditions. We could have just checked the category with the smallest expected proportion.*

9.  **Check the conditions for using the Chi-square distribution to test our hypotheses.**

+ Independent Observations: the ethnic origin of one resident does not tell us about the ethnic origin of another resident (assuming separate households/families)

+ Expected counts are all greater than 5.

Therefore, conditions are not violated!

10. **Carry out the Chi-square Goodness of Fit Test and find the p-value for investigating this research question.**

```{r chisq-goodness-of-fit}
# CAUTION: Pay close attention to the order in the p = c() input.
chisq_test(x = ca_sample,
           response = origin,
           p = c(0.02,0.38,0.03,0.1,0.06,0.41),
           correct = FALSE
)
```

11. **From the output, identify the observed test statistic, degrees of freedom, and p-value.**

    Answer goes here.

12. **At an $\alpha = 0.05$, write a conclusion in the context of the research question.**

    Answer goes here.

