---
title: "R Lab 3: Chi-square Goodness of Fit Test in R"
subtitle: "Which music platform rules the city?"
author:
  - "Team Captain: NAME HERE"
  - "Facilitator: NAME HERE"
  - "Recorder: NAME HERE"
  - "Resource Manager: NAME HERE"
date: "DATE HERE"
format: pdf
editor: visual
execute:
  echo: true
  error: true
  message: false
  warning: false
---

0.  **Load the `infer` package below `library(tidyverse)`**

```{r}
# Load in the packages necessary for our analysis: tidyverse, infer
library(tidyverse)
library(________)
```

A recent market research report claimed that among residents of a large Southern California city, preferences for music streaming platforms were as follows:

**Market Report**

-   Spotify: 41%
-   Apple Music: 38%
-   YouTube Music: 10%
-   Amazon Music: 6%
-   Pandora: 3%
-   Other/Multiple: 2%

A random sample of 1,215 residents was surveyed to see if this distribution still holds true today.

**Research question:** Do the streaming platform preferences of residents differ from those reported in the market research study?

1.  **Read in the data and call it `music_sample.csv`. Additionally, print the top 6 rows to inspect your data.**

```{r}
music_sample <- ____________("music_sample.csv")

```

2.  **What is the observational unit for this study?**

    Answer goes here.

3.  **Create a summary table of the observed counts (number of individuals in the sample who listen to each `platform)`.**

```{r}
# your code goes here. look back at last week's lab!
```

4.  **Notice the ordering of `platform` categories. Why do you think "Amazon Music" is first and "YouTube Music" is last in our list?**

    Answer goes here.

5.  **Using the skills you learned class last week, create a bar plot of the observed *proportions* of individuals in our sample who listen to each music `platform`.**

```{r}
ggplot(data = _________,
       mapping = aes(x = "Observed",
                     fill = _________)
       ) +
  geom_bar(stat = "count",
           position = "__________"
           ) +
  labs(y = "___________________________"
       )
```

6.  **Write the null and alternative hypotheses for investigating this research question.**

    Answer goes here.

7.  **How many of the 1,215 people do we expect to see listening to each platform if the results of the market report accurate? Fill in the table below.**

    |   | Spotify | Apple Music | YouTube Music | Amazon Music | Pandora | Other/Multiple |
    |-----------|-----------|-----------|-----------|-----------|-----------|-----------|
    | **Expected Count** |  |  |  |  |  |  |

*Note: we use the expected counts to check our conditions. We could have just checked the category with the smallest expected proportion.*

8.  **Check the conditions for using the Chi-square distribution to test our hypotheses.**

    Answer goes here.

9.  **Carry out the Chi-square Goodness of Fit Test and find the p-value for investigating this research question. Code only, you will interpret in the next questions.**

```{r}
# CAUTION: Pay close attention to the order in the p = c() input. And don't lose your parentheses!
chisq_test(
  x = ________,
  response = _________,
  p = c(
    
    
    
    
    
  ),
  correct = FALSE
)
```

10. **From the output, identify the observed test statistic, degrees of freedom, and p-value.**

    Answer goes here.

11. **At an** $\alpha = 0.05$, write a conclusion in the context of the research question.

    Answer goes here.
