---
title: "R Lab 4: Nightlight Use and Myopia"
subtitle: "Chi-square Test of Independence"
author:
  - "Team Captain: NAME HERE"
  - "Facilitator: NAME HERE"
  - "Recorder: NAME HERE"
  - "Resource Manager: NAME HERE"
date: "DATE HERE"
format: pdf
editor: source
execute:
  echo: true
  error: true
  message: false
  warning: false
---

```{r setup}
#| include: false
## Load in the packages necessary for our analysis: tidyverse, janitor, infer
library(tidyverse)
library(janitor)
library(infer)
```

In a study reported in *Nature* (Quinn, 1999), a survey of 479 children found that those who had slept with a nightlight or in a fully lit room before the age of two had a higher incidence of nearsightedness (myopia) later in childhood.

In this study, there were two variables studied:

-   `Light`: level of light in room at night (no light, nightlight, full light)
-   `Sight`: level of myopia developed later in childhood (high myopia, myopia, no myopia).

**1. Which variable is the explanatory variable? Which is the response variable?**

Answer goes here.

**2. Read in the data and write code to print out the top 6 rows. What is the observational unit for this study?**

```{r}
# read in data
myopia <- read_csv("data/ChildrenLightSight.csv")

# print top 6 rows

```

**3. Complete the code to visualize the `Light` and `Sight` variables together as a *filled* bar plot.**

```{r}
#| fig-width: 5
#| fig-height: 5

# Code to create the filled barplot
ggplot(data = myopia, 
       mapping = aes(x = ______, 
                     fill = ________)
       ) + 
  geom_bar(position = "_______") + 
  labs(x = "______________", 
       y = "______________", 
       title = "______________")
```

**4. Fill in the code below to generate a contingency table of the counts.**

```{r contingency-table}
myopia |>  
  tabyl(____, ____) |>
  adorn_totals(where = c("row", "col"))
```

**5. How many children slept with a nightlight?**

Answer goes here.

**6. How many children who slept with a nightlight have normal levels of Myopia?**

Answer goes here.

**7. What proportion of children who slept with a nightlight have normal levels of Myopia?** *You may choose to use the code chunk below as a calculator.*

Answer goes here.

```{r}
2 + 2
```

**8. Fill in the code below to generate a contingency table of the *proportions*.**

```{r}
myopia |>  
  tabyl(_____, _____) |> 
  adorn_totals(where = c("row", "col")) |> 
  adorn_percentages(denominator = "____") 
```

**9. Using the filled bar plot and the proportion contingency table above, do you think there is an association between the level of light and the presence of Myopia? Explain your answer.**

Answer goes here.

**10. Write out the null and alternative hypotheses to test whether the level of light is associated with the presence of Myopia.**

Answer goes here.

**11. Check the conditions necessary to use the Chi-square distribution to test our hypotheses.**

Answer goes here.

**12. Complete the code below to conduct a Chi-square Test of Independence.**

```{r}
chisq_test(x = myopia,
           explanatory = _______,
           response = __________,
           correct = FALSE,
           simulate.p.value = ______
           )
```

**13. Write a conclusion in context of the study. Make sure to include your evidence.**

