---
title: "Review Guide for Midterm 2 Exam"
subtitle: "STAT 218: Applied Statistics for Life Science"
embed-resources: true
format:
  html:
    toc: true
  pdf:
    keep-tex: false
    include-in-header:
      text: |
          \usepackage{fancyhdr}
          \pagestyle{fancy}
          \fancyhf{}
          \fancyfoot[C]{\thepage}
          \fancyhead[R]{Stat 218: Review Guide for Midterm 2 Exam}
  docx:
    toc: false
# format: html
# format: docx
# format: revealjs
execute:
  echo: false
  warning: false
  message: false
  error: true
editor: 
  markdown: 
    wrap: 72
---

```{r}
library(tidyverse)
library(mosaic)
library(infer)
```

# What to Expect

-   You may bring an $8 \frac{1}{2} \times 11$ standard sheet of notes
    (both sides). I will not provide you with formulas, so put what you
    think you need on here.
-   You will turn this in with your exam.
-   You may bring any calculator to use. I will have a handful of simple
    calculators. You may **not** use your phone as a calculator.
-   The exam is mostly multiple choice, but will have a couple of short
    answer questions mixed in.
-   You will have 50 minutes to complete the exam.

::: callout-tip
## Canvas Discussion Board

Post any logistic or studying questions on the Canvas discussion board.
Please respond to each other!
:::

# Key Concepts to Review

Note: this may not be an exhaustive list. You should review all of your
notes, assignments, labs, and quizzes from Chapters 4 - 7 (and concepts
that are necessary to build off of from the first three chapters).

-   Can you describe a distribution for a numerical variable? (shape,
    center, spread, outliers)
-   Identify summary statistics (with symbols) from `favstats` output.
-   Identifying pieces of a data set: observation, variable, sample
    size, parameter, etc.
-   Work through hypotheses testing for the following types of scenarios
    (how does parameter wording change, how does the sampling
    distribution change?):
    -   Two categorical variables (Chi-square Test of Independence)
    -   One numerical variable (t-test for a single mean)
    -   Comparing a numerical variable across two **independent** groups
        (two-sample independent t-test)
    -   Comparing a numerical variable across two **dependent** groups
        (paired t-test)
-   Understand the concept of a sampling distribution for
    -   means
    -   differences in means
    -   mean of the differences.
-   Confidence intervals.
    -   How do you find the t-quantile for different confidence levels?
    -   How do confidence intervals and levels relate to hypotheses
        testing?
-   Scope of Inference
    -   How do you know when you can generalize to the population of
        interest? (Random Sampling / a Representative Sample from xxx)
    -   When can you say *causation* versus *association* only? (Random
        Assignment of xxx)
-   How do you interpret the p-value? Can you do this for various
    scenarios?

\newpage

# Practice Problems

*Suggestion: you can "create" your own questions building off of these
scenarios. Ask yourself about causation, generalization, practice
calculating confidence intervals, etc. If not given a t-quantile for
something like this, 2 is typically a good substitute for a 95%
confidence interval multiplier.*

1.  You are thinking of using a t-test to investigate a research
    hypothesis about the mean of a population. The distribution of your
    sample is extremely skewed (i.e., not normally distributed). Which
    of the following statements is most correct?

> a.  You may use the t-test provided your sample size is large (say at
>     least 30 or so).
> b.  You should not use the t-test regardless of the sample size
>     because the population does not have a normal distribution, so the
>     normality assumption won't be met.
> c.  You may use the t-test provided you use a fairly large confidence
>     level, say 99%.
> d.  You may not use the t-test, but a confidence interval constructed
>     using the t-distribution should be valid.


\vspace{0.1in}

2.  A 95% confidence interval for the difference in population means
    between Groups A and B (µA - µB) is given as follows: -3.9 ≤ µA - µB
    ≤ -1.0. Which of the following statements is most correct?

> a.  We have evidence that the mean of Group A is larger than the mean
>     of Group B.
> b.  We have evidence that the mean of Group A is smaller than the mean
>     of Group B.
> c.  We have evidence that the mean of Group A is equal to the mean of
>     Group B.
> d.  We can't tell - we can't draw any conclusions unless we have a
>     p-value.


\vspace{0.1in}

3.  Suppose you are investigating the weight of Snickers bars. Your
    hypotheses are as follows:

> $H_0$: The mean weight for all Snickers bars is 48 grams
> ($\mu = 48$).\
> $H_A$: The mean weight for all Snickers bars is more than 48 grams
> ($\mu > 48$).

You take a random sample of 40 Snickers bars, and you conclude that the
mean weight of all Snickers bars is more than 48 grams with a p-value of
0.02.

\vspace{0.1in}

i.  Which of the following statements best describes what that p-value
    means?

> a.  If the mean weight of all Snickers bars is 48 grams, the
>     probability that a random sample of 40 Snickers would have a mean
>     as high or higher than your sample mean is 0.02.
> b.  If the mean weight of all Snickers bars is more than 48 grams, the
>     probability that a random sample of 40 Snickers would have a mean
>     as high or higher than your sample mean is 0.02.
> c.  Only 2% of all Snickers bars weigh more than 48 grams.
> d.  The probability that the true mean weight of all Snickers bars
>     equals 48 grams is 0.02.

\vspace{0.1in}

ii. Suppose that the standard deviation of your sample was $s = 5g$. The
    standard error (i.e., standard deviation of the sample mean) is:

> a.  8
> b.  5
> c.  0.125
> d.  0.79

\vspace{0.1in}

iii. Suppose a 95% confidence interval is computed to estimate the mean
     weight of all Snickers bars. Which of the following values will
     definitely be within the limits of this confidence interval?

> a.  The population mean, $\mu$.
> b.  The sample mean, $\bar x$.
> c.  The p-value.
> d.  None of the above.

\vspace{0.1in}

4.  An article in the San Luis Tribune claims that the average age for
    people who receive food stamps in SLO is 40 years. A Cal Poly
    student believes the average age is less than that. The student
    obtains a random sample of 100 people in SLO who receive food
    stamps, and finds their average age to be 39.2 years. Performing a
    hypothesis test, the student finds their sample mean to be
    statistically significantly lower than the age of 40 stated in the
    article (p-value \< 0.05). Indicate fore each of the following
    interpretations whether they are valid or invalid.
    
\vspace{0.1in}

i.  The statistically significant result indicates that the majority of
    people who receive food stamps are younger than 40.

-   valid

-   invalid

\vspace{0.1in}

\vspace{0.1in}

ii. An error must have been made. This difference in means (39.2 vs. 40
    years) is too small to be statistically significant.

-   valid

-   invalid

\vspace{0.1in}

5.  Can Tai Chi help improve postural stability in Parkinson's patients?
    To investigate, researchers randomly assigned 65 Parkinson's
    patients to practice Tai Chi daily for 24 weeks, and another 65
    Parkinson's patients to practice stretching daily for 24 weeks. The
    outcome we will focus on is functional reach (measured in cm.).

```{r}
set.seed(1)
parkinsons_data1 <- tibble(Exercise = c(rep("Tai Chi", 65), 
                                        rep("Stretching", 65)
                                        ),
                           Reach = c(rnorm(n = 65, mean = 29.4, sd = 5.5),
                                     rnorm(n = 65, mean = 25.0, sd = 7.3)
                                     )
                           ) |> 
  mutate(Exercise = factor(Exercise, levels = c("Tai Chi", "Stretching")))

favstats(Reach~Exercise, data = parkinsons_data1)
```

i.  Identify the response and explanatory variables (and their types).

\vspace{1in}

ii. Describe a tactile simulation strategy (using either coins, or
    spinners, or cards) to calculate a p-value to investigate whether
    Tai Chi can help improve functional reach in Parkinson's patients.
    Be sure to provide enough details so that anyone could carry out the
    simulation by reading just your description here. (*Hint: Think back
    to the yawn experiment.*)

\vspace{1.2in}

iii. A 95% confidence interval comparing Tai Chi and Stretching was
     calculated from the above data: (2.73, 6.59). Interpret this
     interval in the context of this study.

\vspace{1.2in}

iv. A 99% confidence interval based on the above data would be the 95%
    confidence interval. Circle one.

-   narrower than 95% confidence interval

-   the same as the 95% confidence interval

-   wider than 95% confidence interval

\vspace{0.1in}

v.  Suppose that the observed standard deviations had turned out to be:
    $s_\text{Tai Chi} = 5.8$ and $s_\text{Stretching} = 7.2$. What would be the primary change to the 95% confidence interval be
compared to the original of (2.73, 6.59)?

-   The middle of the interval would be a smaller number

-   The middle of the interval would be a bigger number

-   The width of the interval would be a bigger number

-   The width of the interval would be a smaller number

-   The interval would remain unchanged

\vspace{0.1in}

6.  In 2004, the state of North Carolina released to the public a large
    dataset containing information on births recorded in this state.
    This data set has been of interest to medical researchers who are
    studying the relation between habits and practices of expectant
    mothers and the birth of their children. This analysis will focus on
    a random sample of 1,000 observations from the published dataset.

```{r}
library(openintro)
favstats(weight ~ habit, data = births14)
```

```{r}
births14 |> 
  filter(!is.na(habit)) |> 
  ggplot(mapping = aes(x = weight)) + 
  geom_histogram(binwidth = 1.5, color = "white") + 
  facet_wrap(~habit, scales = "free_y") + 
  theme_bw() +
  labs(x = "Weight of Baby (lbs)", 
       y = "Number of Babies")
```

```{r}
births14 |> 
  filter(!is.na(habit)) |> 
  ggplot(mapping = aes(x = weight,
                       y = habit)) + 
  geom_boxplot() +
  theme_bw() +
  labs(x = "Weight of Baby (lbs)", 
       y = "Mother Habit")
```

i.  Hospital administration at Duke University Hospital are interested
    in the difference in the mean baby birth weight between mothers who
    do not smoke and mothers who do smoke. Using the summary statistics
    above, report the observed statistic for this comparison. Indicate
    in your answer what notation should be used for this statistic.

\vspace{1in}

ii. These hospital administrators are interested in estimating the true
    difference in mean birth weight between mothers who do not smoke and
    mothers who do smoke. The administrators learned in their Statistics
    class how to obtain a confidence interval for a difference in means
    using a $t$-distribution. Using the plots above and your knowledge
    of how the data were collected evaluate whether it would be
    appropriate for the administrators to use a $t$-distribution to
    obtain a confidence interval for the true difference in means.

\vspace{1in}

iii. Select the correct t-quantile from below and construct a 99%
     confidence interval.

`qt(0.95, 959)` = `r qt(0.95, 959)`

`qt(0.975, 959)` = `r qt(0.975, 959)`

`qt(0.99, 959)` = `r qt(0.99, 959)`

`qt(0.995, 959)` = `r qt(0.995, 959)`

\vspace{1in}

iv. Interpret the 99% confidence interval in the context of this study.

\vspace{1in}

v.  Based on your confidence interval above, which of the following is
    the most likely p-value for a two-sided hypothesis test? Circle one.

-   0.20
-   0.10
-   0.05
-   0.005

\vspace{0.1in}

7.  Which of the following analyses is most appropriate for the
    following situation? A teacher compares the pre-test and post-test
    scores of a group of students to test whether their scores have
    increased throughout the semester.

> a.  A paired t-test for dependent samples
> b.  A two-sample t-test for independent samples

\vspace{0.1in}

8.  Which of the following analyses is appropriate for the following
    situation? A random sample of 100 male students and a random sample
    of 1000 female students are asked how many Cal Poly Soccer games
    they attended this past season. The goal is to test whether male Cal
    Poly students attend more football games, on average, than the
    female Cal Poly students.

> a.  A paired t-test for dependent samples
> b.  A two-sample t-test for independent samples

\vspace{0.1in}

9.  Which of the following analyses is appropriate for the following
    situation? Ten diamond rings are shown to two jewelers, and each
    jeweler is asked to determine the appraisal value for each ring. The
    goal is to test whether the two jewelers give different appraisal
    values, on average.

> a.  A paired t-test for dependent samples
> b.  A two-sample t-test for independent samples

\vspace{0.1in}

10. Suppose that in order to investigate the effectiveness of a new
    blood pressure drug, subjects are randomly assigned to either the
    placebo group or the treatment group. All subjects have their blood
    pressure measured at baseline. Those in the placebo group then
    receive an inactive pill for 2 months, and those in the treatment
    group receive the new drug for 2 months. At the end of the two
    months, researchers once again measure each subject's blood pressure
    and compute the change in blood pressure for each subject.

**Research Question** Does the new drug improsve the blood pressure for
all adults?

i.  Sketch out what this data might look like (*Hint: Look back at
    Example 7.3*).

\vspace{3in}

ii. Write out the parameter of interest for the study.

\vspace{1in}

iii. In symbols, set up the null and alternative hypothesis.

\vspace{1in}

iv. Check the conditions necessary to conduct an analysis using the
    t-distribution.

\vspace{1in}

v.  Suppose we obtain a t-statistic of 0.92 and a p-value of 0.17. What
    would your conclusion be in context of the research question?

\vspace{1in}

vi. What is the interpretation of the p-value above in context of the
    problem?

\vspace{1in}

vii. What do you want to know about the subjects in order to generalize
     your results to all adults?

\vspace{1in}

viii. Suppose we had found *evidence* in support of the research
      question. Could we say that the new drug *causes* an improvement
      in blood pressure?
      
\vspace{1in}

11. In a [recent study](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC9831139/) conducted in the United Kingdom, researchers gathered data on 6,705 children to investigate the potential relationship between a mother's exposure to cats during pregnancy and the occurrence of psychotic episodes in their children. The study included two groups: one consisting of 4,746 children whose mothers did not have cats while pregnant and another group of 1,959 children whose mothers did have cats during pregnancy.

Among the group of 4,746 children with no maternal cat exposure, 536 children experienced one or more psychotic episodes during the course of the study. In contrast, among the 1,959 children whose mothers had cats during pregnancy, 240 children had one or more psychotic episodes.

**Research Question:** Does the psychotic episode rate differ between children who's moms did have cats while pregnant and those who's moms did not?

(i) Create a contingency table of counts based on the data obtained in this study.

\vspace{2in}

(ii) Find the observed proportion of children who's moms did not have cats while pregnant that had one or more psychotic episode.

\vspace{1in}

(iii) Find the observed proportion of children who's moms did have cats while pregnant that had one or more psychotic episode.

\vspace{1in}

The following output was obtained from a chi-square test to investigate this question.

```{r simulate-data}
#| echo: false
library(tidyverse)

set.seed(56156)
cats <- tibble(combo = c(rep("nocats-psychotic", 536),
                                 rep("nocats-nopsychotic", 4746-536),
                                 rep("cats-psychotic", 240),
                                 rep("cats-nopsychotic", 1959-240)
                                 )

) |>
  separate_wider_delim(cols = combo, names =  c("cats", "psychotic"), delim = "-")
```

```{r}
#| echo: true
library(infer)
chisq_test(x = cats,
           response = psychotic,
           explanatory = cats)
```

\vspace{1.2in}

(v) Write a solution and make sure to include the chi-square test statistic, degrees of freedom, the p-value, and a conclusion written in everyday language.

\vspace{1.2in}

12.  Ten mice (6--8 weeks old) were randomly assigned to one of two groups; five were exposed to simulated environmental tobacco smoke for 6 h/day, 5 days/week for 5 months. The other 5 mice were kept in clean air during this time period. Then, all of the mice were allowed to recover for a further 4 months in filtered air before being killed for analysis of lung tumor incidence. The results are shown below.

    |             | **Tumor** | No Tumor | Total |
    |-------------|-----------|----------|-------|
    | **Treated** | 4         | 1        | 5     |
    | **Control** | 2         | 3        | 5     |
    | **Total**   | 6         | 4        | 10    |

**Research question:** Does the proportion of mice that develop a lung tumor differ between those exposed to tobacco smoke and the control group?

(i) Convert the Research Question into $H_0$ and $H_A$.

\vspace{1.2in}

(iii). What proportions would you compare to answer the research question?

\vspace{1.2in}

(ii). Would it be appropriate to use the chi-square distribution to test the hypotheses? Explain.

\vspace{1.2in}
