---
title: "Activity 6B: Cholesterol III"
subtitle: "Inference for Paired Data"
format: pdf
# format: html
# format: docx
---


```{r setup, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE, 
                      fig.align = "center",
                      fig.pos = "H")

library(tidyverse)
library(patchwork)
library(mosaic)
library(infer)

set.seed(93401)
```

```{r data-prep, echo = FALSE}

# https://www.sjsu.edu/faculty/gerstman/StatPrimer/paired.pdf

cholesterol_data <- tibble::tribble(
          ~ ID, ~CORNFLK, ~OATBRAN,
                                    "1", "4.61", "3.84",
                                    "2", "6.42", "5.57",
                                    "3", "5.40", "5.85",
                                    "4", "4.54", "4.80",
                                    "5", "3.98", "3.68",
                                    "6", "3.82", "2.96",
                                    "7", "5.01", "4.41",
                                    "8", "4.34", "3.72",
                                    "9", "3.80", "3.49",
                                   "10", "4.56", "3.84",
                                   "11", "5.35", "5.26",
                                   "12", "3.89", "3.73",
                                   "13", "2.25", "1.84",
                                   "14", "4.24", "4.14"
          )

factorCols <- c("ID")
cholesterol_data[,factorCols] <- lapply(cholesterol_data[,factorCols], as.factor)
numericCols <- c("CORNFLK", "OATBRAN")
cholesterol_data[,numericCols] <- lapply(cholesterol_data[,numericCols], as.numeric)

cholesterol_data <- cholesterol_data |> 
  mutate(cholesterolDiff = CORNFLK - OATBRAN)

cholesterol_data_long <- cholesterol_data |> 
  pivot_longer(cols = c(CORNFLK, OATBRAN),
               names_to = "Diet",
               values_to = "Cholesterol")  |> 
       select(Diet, Cholesterol)
```

### Learning outcomes

+ Given a research question involving paired differences, construct the null and alternative hypotheses in words and using appropriate statistical symbols.
  
+ Describe and perform a simulation-based hypothesis test for a paired mean difference.

+ Interpret and evaluate a p-value for a simulation-based hypothesis test for a paired mean difference.

+ Use bootstrapping to find a confidence interval for a paired mean difference.

+ Interpret a confidence interval for a paired mean difference.

+ Use a confidence interval to determine the conclusion of a hypothesis test.

---

## Review from last week

Researchers investigated whether eating corn flakes compared to oat bran had an effect on serum cholesterol levels. Twenty-eight (28) individuals were randomly assigned a diet that included either corn flakes (14 individuals) or oat bran (14 individuals). After two weeks, cholesterol levels (mmol/L) of the participant were recorded.

## Vocabulary Review

1.  Identify the variables in this study.  What role (explanatory or response)
do each have?

\vspace{0.5in}

2. Are the **differences** in AQI scores independent for each case (US city)? 
Explain.

\vspace{0.5in}

3. Why is this treated as a paired study design and not two independent samples?

\vspace{0.5in}

## Ask a Research Question

4. What are the two competing possibilities for explaining the differences in 
AQI scores? 

\vspace{0.8in}

5. Write the null hypothesis in **words**.

\vspace{0.8in}

6. What is the research question this study seeks to address?

\vspace{0.8in}

7. Write the alternative hypothesis in **notation**.

\vspace{0.8in}

## Summarize and Visualize the Data

A histogram of the differences in AQI scores for the 33 cities and a table of
summary statistics are shown below. 

```{r histogram}
ggplot(data = air, 
       mapping = aes(x = Difference)) +
  geom_histogram(binwidth = 17) +
  labs(x = "Difference in air quality score (April 2020 - 5 Year Median)") 
```

Summary statistics for the June 2020 (Current) AQI scores, median AQI scores
from 2015--2019, and the differences in AQI scores.

```{r}
air %>%
  pivot_longer(cols = Current:Difference, 
               names_to = "time_period", 
               values_to = "AQI") %>% 
  mutate(time_period = fct_relevel(time_period, 
                                   "Current", 
                                   "5yearMedian", 
                                   "Difference"
                                   )
         ) %>% 
  group_by(time_period) %>% 
  summarize(mean = mean(AQI), 
            sd = sd(AQI)
  ) %>% 
  rename(Mean = mean, 
         `Standard Deviation` = sd, 
         Variable = time_period) %>% 
  pander()
```

\newpage

8. Report the summary statistic of interest (mean difference) for the data.  

\vspace{0.3in}

9. What notation is used for the value in question 8? 

\vspace{0.3in}

## Use Statistical Methods to Draw Inferences from the Data 

### Hypothesis Test 

To simulate the null distribution of paired sample mean differences we need 
to randomly assign the AQI score for each city to be either the current value or
the five year median. 

Take for example Albuquerque, New Mexico. In April 2020 the current AQI score was
23 and the five year median was 30. If we assume the null is true, that the mean
of the differences is 0, then there is no relationship between Albuquerque's 
AQI score and the time period. That means, Albuquerque would have been just as 
likely to see an AQI score of 30 in April of 2020. 

10. How can we use a coin to decide which values for each city are randomly
assigned to the "Current" (April 2020) time period? 

\vspace{1in}

A simulated null distribution is shown below. 

```{r null-dist, warning = FALSE}
null_dist <- air %>% 
  specify(response = Difference) %>% 
  hypothesise(null = "point", mu = 0) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")

null_dist %>% 
  visualise() + 
  labs(title = "", 
       x = "Simulated Mean Difference")
```

11. Explain why the null distribution is centered at zero. 

\newpage

12. Find the observed mean difference on the distribution. 

\vspace{0.1in}

13. Shade the area of the distribution you will use to calculate the p-value. 

\vspace{0.1in}

14. Estimate the p-value for testing if there was improved air quality in US
cities in April 2020. 

\vspace{0.25in}

15. How much evidence does this provide for improved air quality in US cities?

\vspace{0.5in}

16. If evidence was found for improved air quality in US cities, could we
conclude that the stay-at-home directives ***caused*** the improvement in air
quality? Explain.

\vspace{1in}

## Confidence Interval

The goal of a confidence interval is to estimate a plausible range of values for
the population parameter. 

17. What is the population parameter in this study?

\newpage

To create a bootstrap distribution, we **do not** assume the null hypothesis is
true. Instead, we assume that the difference in AQI scores for these 33 US
cities are representative of the differences in AQI scores for other US cities.
So, we will randomly sample, with replacement, from our original sample to
obtain a bootstrap sample. 

I've created a bootstrap distribution below, using 1000 reps. 

```{r boot-dist}
boot_dist <- air %>% 
  specify(response = Difference) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")

boot_dist %>% 
  visualise() + 
  labs(title = "", 
       x = "Bootstrap Mean Difference")
```

18. Where is the bootstrap distribution be centered? Why is it centered there?

\vspace{0.5in}

19. Use the table below to find a 99% confidence interval for $\mu_{\text{diff}}$. 

\vspace{0.5in}

```{r percentile-ci}
boot_dist %>% 
  summarize("0.5%" = quantile(stat, 0.05), 
            "1%" = quantile(stat, 0.01),
            "2.5%" = quantile(stat, 0.025),
            "5%" = quantile(stat, 0.05),
            "90%" = quantile(stat, 0.90),
            "95%" = quantile(stat, 0.95),
            "97.5%" = quantile(stat, 0.975),
            "99.5%" = quantile(stat, 0.95)
            ) %>% 
  pivot_longer(cols = everything(), 
               names_to = "Quantile", 
               values_to = "Value") %>% 
  pander()
```


## Communicate the Results and Address the Research Question

20. Interpret the 99% confidence interval in the context of the problem.

\vspace{1in}


21. Do the results of your confidence interval and hypothesis test agree? What
does each tell you about the null hypothesis?

\vspace{1in}

---

## Take-home messages

1.	The differences in a paired data set are treated like a single quantitative
variable when performing a statistical analysis.  Paired data (or paired
samples) occur when pairs of measurements are collected. We are only interested
in the population (and sample) of **differences**, and not in the original data. 

3. When analyzing paired data, the summary statistic is the "mean difference"
**not** the "difference in means"^[Technically, if we calculate the differences
and then take the mean (mean difference), and we calculate the two means and
then take the difference (difference in means), the value will be the same.
However, the *sampling variability* of the two statistics will differ, as we
will see in the next activity].  This terminology will be *very* important in
interpretations.

4. To create one simulated sample on the null distribution for the mean
difference, we focus on each observation **not** on the groups of observations. 
For each observation, we flip a coin to decide which response value goes first
and which goes second. We do this for **every** observation. Once we've randomly
assigned which observation comes first, we find the difference in the values for
each observation. Finally, we calculate and plot the simulated mean difference.

5. To create one simulated sample on the bootstrap distribution for a sample
mean or mean difference, label $n$ cards with the original values / differences.
Randomly draw with replacement $n$ times.  Calculate and plot the resampled mean
or mean difference.