---
title: "R Lab 1: Introduction to Data in R"
author:
  - "Team Captain: NAME HERE"
  - "Facilitator: NAME HERE"
  - "Recorder: NAME HERE"
  - "Resource Manager: NAME HERE"
date: "DATE HERE"
format: pdf
editor: source
execute:
  echo: true
---

```{r}
#| label: setup
#| include: false
library(readr)
library(ggplot2)
```

## Remember -- Question the Arson

You can load data files into R using functions from different packages. Typically, we will work with data that are stored in a Comma Separated Values file (a .csv). For this format of data, we will use the `read_csv()` function to read in our data.

The data are located in the *data* folder of your project (see bottom right files tab). To load in the data, we need to specify the "path" to the data, or where R needs to look for the data. I'll walk you through what the code below is doing.

-   `arson_data` is the name of the object we are storing the data set into. This is the name R knows the data set by.
-   The `<-` "assigns" the output of the `read_csv()` function into the `arson` object
-   `read_csv()` is a function that reads in our csv data file
-   `"data"` is the name of the sub-folder the data live in (look in the bottom right of your RStudio IDE)
-   `"arson.csv"` is the name of the data set. This is the name Posit Cloud's data sub-folder knows the data set by.

```{r}
#| label: read-data
#| include: false
arson_data <- read_csv("data/arson.csv")
```

1.  **Write code to preview the top 6 rows of the arson data set.**

    The recorder should type the answer here.

```{r}
#| label: preview-arson-data

# To run the code, hit the green "play" button in the top right of this code chunk.
# You should type code for question 5 below this line.

```

2.  **What are the observations in this data set?**
    
    The recorder should type the answer here.
    
3.  **How many observations are there in the data set?** *Hint: you can use code to find this or look in the top right environment.*

    The recorder should type the answer here.

4.  **What are the variables in this data set? What are their data types?**

    The recorder should type the answer here.

5.  **How many variables are there in the data set?** *Hint: you can use code to find this or look in the top right environment.*

    The recorder should type the answer here.

You can also embed plots in the rendered document. Here is an example of a plot:

```{r}
#| label: arson-plot
#| echo: false 
# Hit the green "play" button to run the code in the top right.

ggplot(data = arson_data,
       aes(x = Outcome,
           fill = Outcome)
       ) + 
  geom_bar(stat = "count") +
  labs(title = "Arson Suspect Responses",
       x = "Outcome",
       y = "Number of Questions"
       )
```

## Childcare Costs in San Luis Obispo

6. **Load in and preview the SLO childcare data set in the following code chunk. You may need to look in the data folder to find the name of the .csv file.**

```{r}
# Write your code below this line.


# You may choose to write more code below this line to help you answer the next couple of questions.
```

7. **What are the observational units in this data set?**
    
    The recorder should type the answer here.
    
8. **What are the variables in this data set? Also describe what information the variables contain, don't just list the names of the variables.**

    *A description of the data can be found [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-05-09/readme.md).*
    
    The recorder should type the answer here.
    
9. **Suggest one categorical variable that you could measure about the observational units.**

    *It is worth it to note that we don't have data for individual households. Carefully consider your observational unit here.*
    
    The recorder should type the answer here.
    
10. **Could we use this data set to say anything about the cost of childcare in Santa Barbara County? Explain your answer.**
    
    The recorder should type the answer here.
    

