---
title: "Your Title Goes Here! Make it fun and related to your data set!"
subtitle: "Stat 218: Final Project"
author:
  - "Team Captain: NAME HERE"
  - "Facilitator: NAME HERE"
  - "Recorder: NAME HERE"
  - "Resource Manager: NAME HERE"
date: "DATE HERE"
format: pdf
editor: source
execute:
  echo: true
  error: true
  message: false
  warning: false
---

<!-- Note, anything in green is a comment and will not show when your document is rendered. Please type your material below the green comments. -->

```{r}
#| label: true
#| include: false
# The code to load in the necessary packages goes here!
# You will need: tidyverse, mosaic, and moderndive
```

-   DATA SET NAME: <copy paste link to data set here>

```{r read-data}
## This is where you will read in your data! 
# I suggest copying and pasting code from a prior lab. 
# You will need to change: 
# 1. the name of the dataset (you get to choose the name)
# 2. directions for how to get to the data (is it in a data folder? is it in the main folder?)

```

```{r clean-data}
## Replace the DATA NAME with your data set name after reading in the data. This will make sure the names in your data set are all "clean" -- no spaces, all lowercase, etc. 
DATA NAME <- DATA NAME |> 
  janitor::clean_names()
```

```{r print-data}
## Print the top 6 rows of your data set
```

## Data Description

<!-- In this section you are to describe your data set! Include the following components in your paragraph description. -->
<!-- Describe the context of your data set **in your own words**! Make sure to tell me where the data set came from, what an observational unit is, and what variables / information is stored in the data set. -->
<!-- Tell me why your group picked this data set. -->
<!-- Describe the two quantitative variables you are interested in. Which is the the explanatory variable and which is the response? What do you expect the relationship to be? -->

Your data set description goes here. This should be a paragraph and read like a report.

## Data Visualization

<!-- In this section you will create three visualizations of your data -->

### Histogram of EXPLANATORY VARIABLE NAME

```{r}
## Code to make your second histogram goes here! 
## Don't forget to choose nice binwidths and an axis title!
```

<!-- Describe what you see in the histogram. Your description must include the following components: center, spread, shape, outliers. Your group may choose to additionally run the favstats() function to get summary statistics for this variable.  -->

Describe the histogram of the explanatory variable here.

### Histogram of RESPONSE VARIABLE NAME

```{r}
## Code to make your first histogram goes here! 
## Don't forget to choose nice binwidths (be dramatic) and axis titles!
```

<!-- Describe what you see in the histogram. Your description must include the following components: center, spread, shape, outliers. Your group may choose to additionally run the favstats() function to get summary statistics for this variable. -->

Describe the histogram of the response variable here.

### Scatterplot of RESPONSE VARIABLE NAME and EXPLANATORY VARIABLE NAME

```{r}
## Code to make your scatterplot goes here! 
## Don't forget to choose nice axis labels!
```

<!-- Here is where you describe what you see in the scatterplot. Your description must include the following components: direction, shape, strength, outliers -->

Describe scatterplot here.

## Linear Relationship Between RESPONSE VARIABLE NAME and EXPLANATORY VARIABLE NAME

### Model Conditions

<!-- Here is where you describe the four conditions (LINE) for linear regression.  -->
<!-- State what the condition is and if you believe it is / is not violated IN THE CONTEXT OF YOUR DATA! -->

Put conditions here. This should be in a paragraph form with complete sentences.

### Coefficient Estimates

```{r lm}
## Code to fit a linear regression (note this, is different from adding the line to the scatterplot).
```

```{r coefs}
## Code to get coefficient table from linear regression
```

<!-- Make sure to type the equation (in context of your data) and interpret the coefficients in context of your data set here. -->

Put paragraph with equation and interpretations of coefficients here.

### Inference for the Slope

<!-- Describe the hypothesis test and results for whether the slope is 0.  Make sure to include all parts necessary for a hypothesis test from setup to conclusion. Make sure to use context of your data.  -->
<!-- Describe the confidence interval for the true slope.  Make sure to use context of your data.-->

Put slope hypothesis test and interpretation of confidence interval paragraph here.

