---
title: "Stat 218 Introduction to Data"
author: "Dr. Emily Robinson"
date: "California Polytechnic State University"
output:
  xaringan::moon_reader:
    seal: false
    includes:
      after_body:
        "js-addins.html"
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML"
    # css: ["default", "rladies-fonts", "css/modal.css", "css/this-presentation.css"]
    css: ["default", "metropolis-fonts", "metropolis" ,"css/modal.css", "css/sizeformat.css"]
    # css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightlines: true
      countIncrementalSlides: false
      ratio: "16:9"
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
---
class:title-slide-custom

<style>
p.caption {
  font-size: 0.8em;
}
</style>

```{r, child = "style.Rmd"}
```


```{r setup, echo = FALSE, message = FALSE, warning = FALSE}

# Packages
library(emoji)
library(tidyverse)
library(gridExtra)
library(scales)
library(knitr)
library(kableExtra)
library(iconr)
library(fontawesome)
library(readr)
library(patchwork)

# R markdown options
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      cache = FALSE,
                      fig.align = 'center',
                      dpi = 300)
options(htmltools.dir.version = FALSE)
options(knitr.kable.NA = '')
```

```{r, include = F, eval = T, cache = F}
clean_file_name <- function(x) {
  basename(x) %>% str_remove("\\..*?$") %>% str_remove_all("[^[A-z0-9_]]")
}
img_modal <- function(src, alt = "", id = clean_file_name(src), other = "") {
  
  other_arg <- paste0("'", as.character(other), "'") %>%
    paste(names(other), ., sep = "=") %>%
    paste(collapse = " ")
  
  js <- glue::glue("<script>
        /* Get the modal*/
          var modal{id} = document.getElementById('modal{id}');
        /* Get the image and insert it inside the modal - use its 'alt' text as a caption*/
          var img{id} = document.getElementById('img{id}');
          var modalImg{id} = document.getElementById('imgmodal{id}');
          var captionText{id} = document.getElementById('caption{id}');
          img{id}.onclick = function(){{
            modal{id}.style.display = 'block';
            modalImg{id}.src = this.src;
            captionText{id}.innerHTML = this.alt;
          }}
          /* When the user clicks on the modalImg, close it*/
          modalImg{id}.onclick = function() {{
            modal{id}.style.display = 'none';
          }}
</script>")
  
  html <- glue::glue(
     " <!-- Trigger the Modal -->
<img id='img{id}' src='{src}' alt='{alt}' {other_arg}>
<!-- The Modal -->
<div id='modal{id}' class='modal'>
  <!-- Modal Content (The Image) -->
  <img class='modal-content' id='imgmodal{id}'>
  <!-- Modal Caption (Image Text) -->
  <div id='caption{id}' class='modal-caption'></div>
</div>
"
  )
  write(js, file = "js-addins.html", append = T)
  return(html)
}
# Clean the file out at the start of the compilation
write("", file = "js-addins.html")
```

<br><br>
# INTRODUCTION TO DATA & STATISTICAL INFERENCE
## Stat 218: Applied Statistics for the Life Sceinces
#### Dr. Emily Robinson 
#### California Polytechnic State University - San Luis Obispo
##### `r fa("github", fill = "black")` [Course GitHub Webpage](https://earobinson95.github.io/stat218-calpoly)

---
class:primary
# SEPTEMBER 19, 2022

 Today we will...

`r fa_i("chart-bar")` RStudio Cloud Setup

---
class:primary
# TO DO

+ Introduction Questionnaire *(due ...)*
+ Lab 1: Welcome to RStudio Cloud *(due)*

